---
title: "Data prep script 2: Compute NIH TOolbox Flanker Score"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script computes the NIH Toolbox Flanker score

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80, Ncpus = 6) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  # renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(MASS)       #calculate residualized scores
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
LDDM_cleaning04_fullbeh_d1 <- read.csv(here("../DDM_Trialwise_Prepped/Old/StTr_S1_ERN_HDDM_data_acc_coded.csv"))

LDDM_cleaning04_fullbeh_d2 <- read.csv(here("../DDM_Trialwise_Prepped/Old/StTr_S2_ERN_HDDM_data_acc_coded.csv"))
```

## 3.1 Day 1
```{r}
# Setup the dataset with the needed variables (eg., ID, block # 1-11, trial # 1-30 per block)
LDDM_cleaning04_d1_calc1 <- LDDM_cleaning04_fullbeh_d1 %>%
  group_by(subj_idx) %>%
  mutate(block = c(rep(1,30),rep(2,30),rep(3,30),rep(4,30),rep(5,30),rep(6,30),rep(7,30),rep(8,30),rep(9,30),rep(10,30),rep(11,30))) %>%
  group_by(subj_idx, block) %>%
  mutate(trial = 1:30)

# Calculate the accuracy per subject (according to NIH toolbox this should be the number of correct responses * 5/total trials (330))
LDDM_cleaning04_d1_calc2 <- LDDM_cleaning04_d1_calc1 %>%
  group_by(subj_idx) %>%
  summarise(accuracy_score = sum(response==1)*(5/length(trial)))

LDDM_cleaning04_d1_ind <-  LDDM_cleaning04_d1_calc1 %>%
  group_by(subj_idx) %>% # per subject
  filter(stim=="incongruent" & response==1) %>% #incongruent trials with correct response
  mutate(mean_rt = mean(rt),
         sd_rt = sd(rt)) %>% # compute individual mean and sd RT
  filter(rt>=0.1 & rt>(mean_rt - 3*sd_rt) & rt<(mean_rt + 3*sd_rt)) %>% #remove trials less than 100ms and less than 3SD below or 2SD above the mean RT
  summarise(med_rt = median(rt)*1000) %>% # compute individual level median RT
  mutate(rt_score = 5-(5*((log(med_rt)-log(250))/(log(1000)-log(250)))))

LDDM_cleaning04_d1_calc3 <- LDDM_cleaning04_d1_calc1 %>%
  full_join(LDDM_cleaning04_d1_ind, by = 'subj_idx') %>%
  full_join(LDDM_cleaning04_d1_calc2, by='subj_idx') %>%
  group_by(subj_idx) %>% # per subject
  mutate(total_accuracy_perc = sum(response==1)/length(response)) %>% # compute total accuracy percentage
  summarise(flanker_score_list_d1 = if_else(total_accuracy_perc>=0.8, accuracy_score+rt_score, accuracy_score),
            accuracy = mean(total_accuracy_perc)) %>%# if accuracy is above 80% then add accuracy and rt flanker scores, if not base the flanker score only on accuracy
  transmute(ID=subj_idx, flanker_score_list_d1=flanker_score_list_d1, accuracy=accuracy) %>%
  group_by(ID) %>% # per subject
  summarise(flanker_score_d1 = mean(flanker_score_list_d1),
            accuracy = mean(accuracy))
```

## 3.2 Day 2
```{r}
LDDM_cleaning04_d2_calc1 <- LDDM_cleaning04_fullbeh_d2 %>%
  group_by(subj_idx) %>%
  mutate(block = c(rep(1,30),rep(2,30),rep(3,30),rep(4,30),rep(5,30),rep(6,30),rep(7,30),rep(8,30),rep(9,30),rep(10,30),rep(11,30))) %>%
  group_by(subj_idx, block) %>%
  mutate(trial = 1:30)

LDDM_cleaning04_d2_calc2 <- LDDM_cleaning04_d2_calc1 %>%
  group_by(subj_idx) %>%
  summarise(accuracy_score = sum(response==1)*(5/length(trial)))

LDDM_cleaning04_d2_ind <-  LDDM_cleaning04_d2_calc1 %>%
  group_by(subj_idx) %>% # per subject
  filter(stim=="incongruent" & response==1) %>% #incongruent trials with correct response
  mutate(mean_rt = mean(rt),
         sd_rt = sd(rt)) %>% # compute individual mean and sd RT
  filter(rt>=0.1 & rt>(mean_rt - 3*sd_rt) & rt<(mean_rt + 3*sd_rt)) %>% #remove trials less than 100ms and less than 3SD below or 2SD above the mean RT
  summarise(med_rt = median(rt)*1000) %>% # compute individual level median RT
  mutate(rt_score = 5-(5*((log(med_rt)-log(250))/(log(1000)-log(250)))))

LDDM_cleaning04_d2_calc3 <- LDDM_cleaning04_d2_calc1 %>%
  full_join(LDDM_cleaning04_d2_ind, by = 'subj_idx') %>%
  full_join(LDDM_cleaning04_d2_calc2, by='subj_idx') %>%
  group_by(subj_idx) %>% # per subject
  mutate(total_accuracy_perc = sum(response==1)/length(response)) %>% # compute total accuracy percentage
  summarise(flanker_score_list_d2 = if_else(total_accuracy_perc>=0.8, accuracy_score+rt_score, accuracy_score),
            accuracy = mean(total_accuracy_perc)) %>%# if accuracy is above 80% then add accuracy and rt flanker scores, if not base the flanker score only on accuracy
  transmute(ID=subj_idx, flanker_score_list_d2=flanker_score_list_d2, accuracy=accuracy) %>%
  group_by(ID) %>% # per subject
  summarise(flanker_score_d2 = mean(flanker_score_list_d2),
            accuracy = mean(accuracy))
```


## 1.4. Set seed
```{r}
     set.seed(312)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.


# 4. Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
save(LDDM_cleaning03, file=here("./data/LDDM_cleaning03.RData"))
save(LDDM_cleaning03_d1, file=here("./data/LDDM_cleaning03_d1.RData"))
save(LDDM_cleaning03_d2, file=here("./data/LDDM_cleaning03_d2.RData"))

   # renv::snapshot()   #Take a snapshot of environment
```

