---
title: "Data prep script 2: Importing ERP data"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports and merges the self-report data from the Flanker task of the State-Trait study

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(ggplot2)    #creates plots
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(312)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
LDDM_cleaning01_s1 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Trialwise_Prepped/Old/StTr_S1_ERN_HDDM_data_acc_coded.csv")
LDDM_cleaning01_s2 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Trialwise_Prepped/Old/StTr_S2_ERN_HDDM_data_acc_coded.csv")
LDDM_cleaning01_s3 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Trialwise_Prepped/Old/StTr_S3_ERN_HDDM_data_acc_coded.csv")
LDDM_cleaning01_s4 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Trialwise_Prepped/Old/StTr_S4_ERN_HDDM_data_acc_coded.csv")
LDDM_cleaning01_s5 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Trialwise_Prepped/Old/StTr_S5_ERN_HDDM_data_acc_coded.csv")

# LDDM_cleaning01 <- LDDM_cleaning01_s1 %>%
#     left_join(LDDM_cleaning01_s2, by='subj_idx') %>%
#     left_join(LDDM_cleaning01_s3, by='subj_idx') %>%
#     left_join(LDDM_cleaning01_s4, by='subj_idx') %>%
#     left_join(LDDM_cleaning01_s5, by='subj_idx')

# save(STIB_cleaning02, file="./data/STIB_cleaning02.RData")
```

# Accuracy per day
```{r}
for (time in 1:5) {
  eval(parse(text=paste0("LDDM_cleaning02_s", time, " <- LDDM_cleaning01_s", time, " %>%
    group_by(subj_idx, stim) %>%
    summarise(accuracy = sum(response==1)/sum(response==0 | response==1))")))
  print(eval(parse(text=paste0("sum(LDDM_cleaning02_s", time, "$accuracy<=0.5)"))))
  print(eval(parse(text=paste0("LDDM_cleaning02_s", time, "$subj_idx[LDDM_cleaning02_s", time, "$accuracy<=0.5]"))))
}

LDDM_cleaning02_s5$subj_idx[LDDM_cleaning02_s5$accuracy<=0.5]
LDDM_cleaning02_s1$accuracy[LDDM_cleaning02_s1$subj_idx==71]
LDDM_cleaning02_s2$accuracy[LDDM_cleaning02_s2$subj_idx==71]
LDDM_cleaning02_s3$accuracy[LDDM_cleaning02_s3$subj_idx==71]
LDDM_cleaning02_s4$accuracy[LDDM_cleaning02_s4$subj_idx==71]
LDDM_cleaning02_s5$accuracy[LDDM_cleaning02_s5$subj_idx==71]

LDDM_cleaning02_s5$accuracy[LDDM_cleaning02_s5$subj_idx==72]
```

# Reaction timee
```{r}
hist(LDDM_cleaning01_s1[-611,]$rt)

LDDM_cleaning02_s1 <- LDDM_cleaning01_s1 %>%
  filter(rt < 999)
```



# 2 Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
   renv::snapshot()   #Take a snapshot of environment
```

