---
title: "Data prep script 2: Importing ERP data"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports and merges the self-report data from the Flanker task of the State-Trait study

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80, Ncpus = 6) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  # renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(MASS)       #calculate residualized scores
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(workflowr)  #helps with workflow
```

## 1.3. Get the Working Directory
```{r}
  here()
```

## 1.4. Set seed
```{r}
     set.seed(312)    #Set seed
```

## 1.5 Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
LDDM_cleaning02_DDM1 <- read.csv(here("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Results/Block_Based_Day1/Flanker_StTr_S1_Blocks_acc_avtz_DO_v.csv"))
LDDM_cleaning02_DDM1$ID <- LDDM_cleaning02_DDM1$id

LDDM_cleaning02_DDM2 <- read.csv(here("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/DDM_Results/Block_Based_Day2/Flanker_StTr_S2_Blocks_DO_v.csv"))
LDDM_cleaning02_DDM2$ID <- LDDM_cleaning02_DDM2$id

LDDM_cleaning02_frac_prak_latency <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/eeg_processing/erppath/frac_peak_latency_p3_200800.csv")[,1:14]
LDDM_cleaning02_frac_prak_latency <- LDDM_cleaning02_frac_prak_latency %>% 
  rename_with(~paste0(., "_fpl"), contains("bin"))

LDDM_cleaning02_mean_amplitude_ERN_CRN_080 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/eeg_processing/erppath/mean_amplitude_ERN_CRN_080.csv")[,1:14]
LDDM_cleaning02_mean_amplitude_ERN_CRN_080 <- LDDM_cleaning02_mean_amplitude_ERN_CRN_080 %>% 
  rename_with(~paste0(., "_080"), contains("bin"))

LDDM_cleaning02_mean_amplitude_ERN_CRN_0100 <- read.csv("/Volumes/fsmresfiles/PBS/Stewarts/State Trait Study/current_studies/Letkiewicz_DDM/eeg_processing/erppath/mean_amplitude_ERN_CRN_0100.csv")[,1:14]
LDDM_cleaning02_mean_amplitude_ERN_CRN_0100 <- LDDM_cleaning02_mean_amplitude_ERN_CRN_0100 %>% 
  rename_with(~paste0(., "_0100"), contains("bin"))

LDDM_cleaning02_erp <- LDDM_cleaning02_frac_prak_latency %>%  
  left_join(LDDM_cleaning02_mean_amplitude_ERN_CRN_080, by=c('ID','Session')) %>%
  left_join(LDDM_cleaning02_mean_amplitude_ERN_CRN_0100, by=c('ID','Session'))

LDDM_cleaning02 <- LDDM_cleaning02_DDM1 %>%
  left_join(LDDM_cleaning02_DDM2, by='ID') %>%
  left_join(LDDM_cleaning02_erp, by='ID')

save(LDDM_cleaning02, file=here("./data/LDDM_cleaning02.RData"))
```

### 1.5.1 Non-DMM Flanker behavioral RT
```{r}
LDDM_cleaning02_rt <- read_sav(here("./data/**STTR_master_6.6.18_clean_ERN_PE_LPPbehav**.sav"))
LDDM_cleaning02_rt <-  LDDM_cleaning02_rt %>%
  select("ID",matches("Correct|Errors")) %>%
  select(-matches('neut|mut|erot'))
save(LDDM_cleaning02_rt, file="./data/LDDM_cleaning02_rt.RData")
```

# 1. Select only days 1 and 2
```{r}
LDDM_cleaning03 <- LDDM_cleaning02

colnames(LDDM_cleaning03) <- sub('bin5_|bin7_|bin3_|bin4_', '', colnames(LDDM_cleaning03))
colnames(LDDM_cleaning03) <- sub('Congruent_arrow_followed_by_correct', 'Congruent', colnames(LDDM_cleaning03))
colnames(LDDM_cleaning03) <- sub('Incongruent_arrow_followed_by_correct', 'Incongruent', colnames(LDDM_cleaning03))
colnames(LDDM_cleaning03) <- sub('__', '_', colnames(LDDM_cleaning03))


LDDM_cleaning03_d1 <- LDDM_cleaning03 %>%
  filter(Session==1)

LDDM_cleaning03_d2 <- LDDM_cleaning03 %>%
  filter(Session==2)
```

# 3. Create residualized scores
```{r}
electrodes_list <- c("FZ","CZ","FCZ","CPZ","PZ","POZ")
time_windows <- c("080","0100")

# Calculate residualized ERN and difference score ERN (for verification of direction)
for (ex in electrodes_list[1:3]){ 
  for (tw in time_windows){ 
    for (days in c(1,2))
    eval(parse(text=paste0('LDDM_cleaning03_d',days,'$',ex,'_ERN_',tw,' <- stdres(lm(Error_',ex,'_',tw,' ~ Correct_',ex,'_',tw,', LDDM_cleaning03_d',days,', na.action=na.exclude))')))
    eval(parse(text=paste0('LDDM_cleaning03_d',days,'$',ex,'_ERN_diff',tw,' <- LDDM_cleaning03_d',days,'$Error_',ex,'_',tw,' - LDDM_cleaning03_d',days,'$Correct_',ex,'_',tw)))
  }
}

# Calculate residualized P3 onset
for (ex in electrodes_list[4:6]){
      for (days in c(1,2)) {
        eval(parse(text=paste0('LDDM_cleaning03_d',days,'$',ex,'_P3_onset <- stdres(lm(Incongruent_',ex,'_fpl ~ Congruent_',ex,'_fpl, LDDM_cleaning03_d',days,', na.action=na.exclude))')))
      }
}
```


# 4. Closing out
  In this step, go ahead and close out of the file and quit R without saving  
  the work space.
```{r}
save(LDDM_cleaning03, file=here("./data/LDDM_cleaning03.RData"))
save(LDDM_cleaning03_d1, file=here("./data/LDDM_cleaning03_d1.RData"))
save(LDDM_cleaning03_d2, file=here("./data/LDDM_cleaning03_d2.RData"))

   # renv::snapshot()   #Take a snapshot of environment
```

