---
title: "Data prep script 1: Importing ERP data"
author: "Brent Rappaport"
date: "`r format(Sys.time(),  '%Y-%m-%d')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Template Rmd
editor_options:
  chunk_output_type: console
toc: yes
---

# About
This script imports and merges the self-report data from the Flanker task of the State-Trait study

# 1. Get Setup
## 1.1. Clear everything & set width
```{r echo=TRUE, results='hide', message=FALSE}
    options(width=80, Ncpus = 6) #Set width
    rm(list=ls())     #Remove everything from environment
    cat("\014")       #Clear Console
    set.seed(312)
```

## 1.2. Load Libraries
```{r echo=TRUE, results='hide', message=FALSE}
  # renv::restore()     #restore environment
  library(knitr)      #allows rmarkdown files
  library(haven)      #helps import stata
  library(questionr)  #allows lookfor function
  library(MASS)       #calculate residualized scores
  library(tidyverse)  #plotting/cleaning, etc.
  library(broom)      #nice statistical output
  library(here)       #nice file paths
  library(expss)      #labeling variables/values
  library(psych)      #used for statistical analyses
  library(workflowr)  #helps with workflow
```

## Load Data
Remember to immediately rename and remove. Avoid overwriting old data.
```{r}
here::i_am("work/management/data01_LDDM.Rmd")

# LDDM_cleaning02_DDM1 <- read.csv(here("DDM_Results/Block_Based_Day1/Day1_Block11_Alternative_Models.csv"))
LDDM_cleaning02_DDM1 <- read.csv(here("work/data/StTr_S1_ERN_acc_B11_avtz_DO_vta_sdvz.csv")) %>%
  filter(SubID < 90)
LDDM_cleaning02_DDM1$ID <- LDDM_cleaning02_DDM1$SubID

# LDDM_cleaning02_DDM2 <- read.csv(here("DDM_Results/Block_Based_Day2/Day2_Block11_Alternative_Models_original.csv"))
LDDM_cleaning02_DDM2 <- read.csv(here("work/data/StTr_S2_ERN_acc_B11_avtz_DO_vta_sdvz.csv")) %>%
  filter(SubID < 90)
LDDM_cleaning02_DDM2$ID <- LDDM_cleaning02_DDM2$SubID

# LDDM_cleaning02_DDM3 <- read.csv(here("DDM_Results/Block_Based_Day2/Day2_Block11_Alternative_Models_original.csv"))
LDDM_cleaning02_DDM3 <- read.csv(here("work/data/StTr_S3_ERN_acc_B11_avtz_DO_vta_sdvz.csv")) %>%
  filter(SubID < 90)
LDDM_cleaning02_DDM3$ID <- LDDM_cleaning02_DDM3$SubID

# LDDM_cleaning02_frac_prak_latency <- read.csv(here("eeg_processing/erppath/frac_peak_latency_p3_200800.csv"))[,1:15]
# LDDM_cleaning02_frac_prak_latency <- LDDM_cleaning02_frac_prak_latency %>% 
#   rename_with(~paste0(., "_fpl"), contains("bin"))

LDDM_cleaning02_mean_amplitude_ERN_CRN_080 <- read.csv(here("eeg_processing/erppath/mean_amplitude_ERN_CRN_080.csv"))[,1:15] %>% 
  rename_with(~paste0(., "_080"), contains("bin")) %>%
  pivot_wider(id_cols="ID",names_from="Session",values_from = c("bin3_Correct__FCZ_080","bin4_Error__FCZ_080"),
              names_prefix = "d")

# LDDM_cleaning02_mean_amplitude_ERN_CRN_0100 <- read.csv(here("eeg_processing/erppath/mean_amplitude_ERN_CRN_0100.csv"))[,1:15]
# LDDM_cleaning02_mean_amplitude_ERN_CRN_0100 <- LDDM_cleaning02_mean_amplitude_ERN_CRN_0100 %>% 
#   rename_with(~paste0(., "_0100"), contains("bin"))

# Merge all ERP measurements together (P3 onset, Error amplitude, Correct amplitude)
# LDDM_cleaning02_erp <- LDDM_cleaning02_frac_prak_latency %>%  
#   left_join(LDDM_cleaning02_mean_amplitude_ERN_CRN_080, by=c('ID','Session')) %>%
#   left_join(LDDM_cleaning02_mean_amplitude_ERN_CRN_0100, by=c('ID','Session'))

# Merge all three days of DDM data with ERP data
LDDM_cleaning03_d1 <- LDDM_cleaning02_DDM1 %>%
  left_join(select(LDDM_cleaning02_mean_amplitude_ERN_CRN_080, "ID", ends_with("_d1")), by='ID')
LDDM_cleaning03_d2 <- LDDM_cleaning02_DDM2 %>%
  left_join(select(LDDM_cleaning02_mean_amplitude_ERN_CRN_080, "ID", ends_with("_d2")), by='ID')
LDDM_cleaning03_d3 <- LDDM_cleaning02_DDM3 %>%
  left_join(select(LDDM_cleaning02_mean_amplitude_ERN_CRN_080, "ID", ends_with("_d3")), by='ID')

# save(LDDM_cleaning02, file=here("work/data/LDDM_cleaning02.RData"))
```

### 1.5.1 Non-DMM Flanker behavioral RT
```{r}
LDDM_cleaning02_rt <- read_sav(here("work/data/STTR_master_6.6.18_clean_ERN_PE_LPPbehav.sav"))
LDDM_cleaning02_rt <-  LDDM_cleaning02_rt %>%
  select("ID",matches("Correct|Errors")) %>%
  select(-matches('neut|mut|erot'))
save(LDDM_cleaning02_rt, file=here("work/data/LDDM_cleaning02_rt.RData"))
```

# 1. Select only days 1 and 2 and 3
And remove extraneous info in the variables names.
```{r}
remove_prefixes <- function(data) {
colnames(data) <- sub('bin5_|bin7_|bin3_|bin4_', '', colnames(data))
colnames(data) <- sub('Congruent_arrow_followed_by_correct', 'Congruent', colnames(data))
colnames(data) <- sub('Incongruent_arrow_followed_by_correct', 'Incongruent', colnames(data))
colnames(data) <- sub('__', '_', colnames(data))
}
colnames(LDDM_cleaning03_d1) <- remove_prefixes(LDDM_cleaning03_d1)
colnames(LDDM_cleaning03_d2) <- remove_prefixes(LDDM_cleaning03_d2)
colnames(LDDM_cleaning03_d3) <- remove_prefixes(LDDM_cleaning03_d3)
```

# 3. Create residualized scores
```{r}
sessions <- c(1,2,3)

# Calculate residualized ERN and difference score ERN (for verification of direction)
for (days in sessions) {
    eval(parse(text=paste0('
    LDDM_cleaning03_d',days,'$FCZ_ERN_080 <- stdres(lm(Error_FCZ_080_d',days,' ~ 
    Correct_FCZ_080_d',days,', LDDM_cleaning03_d',days,', na.action=na.exclude))'
                           )))
    eval(parse(text=paste0('
    LDDM_cleaning03_d',days,'$FCZ_ERN_diff080 <- 
    LDDM_cleaning03_d',days,'$Error_FCZ_080_d',days,' - LDDM_cleaning03_d',days,'$Correct_FCZ_080_d',days
                           )))
}
```

# 4. Closing out
  In this step, go ahead and close out of the file and quit R without saving the work space.
```{r}
# save(LDDM_cleaning03, file=here("work/data/LDDM_cleaning03.RData"))
save(LDDM_cleaning03_d1, file=here("work/data/LDDM_cleaning03_d1.RData"))
save(LDDM_cleaning03_d2, file=here("work/data/LDDM_cleaning03_d2.RData"))
save(LDDM_cleaning03_d3, file=here("work/data/LDDM_cleaning03_d3.RData"))
```

